Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2022-03-18 Paper/Manuscript.tex
Small fixes to paper

As a metallic sphere is a rather simple and ideal scatterer, we use $\sv$ from a school of non-swimbladdered fish (\textit{tobis}) (fig.~\ref{Fig_Sv_echogram}) to illustrate the processes to obtain $Sv(m)$.

>>>>

As a metallic sphere is a rather simple and ideal scatterer, we use $\sv$ from a school of non-swimbladdered fish (\textit{tobis}) (fig.~\ref{Fig_Sv_echogram}) collected with a 120 kHz centre frequency transducer to illustrate the processes to obtain $S_v(m)$.
